### 2014-06-25 tex/main-body-text.tex
fixed compression issue on Fig2, now it is less ugly

The allocation of indivividuals into K clusters was similar for each program. For all six groups 
of runs from \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

@@

\begin{figure*}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=25em]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}

>>>>

We did not observe major differences among the 
allocation of indivividuals into K clusters between each program. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for \textit{k} of 2, two  
runs yielded identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

@@

\begin{figure*}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=25em]{images/Figures-Pat/Fig2.eps}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}
